pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-21 article.tex
Show experiment setup of first research question

The second step is to select how an inference model is picked.
We just select the generative model, which consists in a collection of 
three elements: a site model, clock model and tree prior. 
If we know how the generative model of the alignment, as we did above,
we can re-use that information. We do still need to specify 
a generative tree prior, which is the tree prior underlying the phylogeny.
In this case, we'll pick a (constant-rate) birth-death model:

>>>>

In the second step we state our experiments. In this context, we
define an experiment as a combination of an inference model
and the conditions under which a Bayesian inference is created.

\begin{table}
  \begin{tabular}{ | c | c | c | l | }
    \hline
    \textbf{model type} & \textbf{run if} & \textbf{measure evidence} & \textbf{inference model} \\ 
    \hline
    generative & always & no & generative model \\
    \hline
  \end{tabular}
  \caption{Experimental setup to answer the first research question}
\end{table}

If we know how the generative model of the alignment, as we did above,
we can re-use that information. We do still need to specify 
a generative tree prior, which is the tree prior underlying the phylogeny.
In this case, we'll pick a (constant-rate) birth-death model:
